prep_annotating

### 2022-12-07 code/prep_annotate.Rmd
work on draft cogsci figs, much sbert
rerun sbert post test

#filter(annotated,span_good==F)  |> View() #Note: dowm from more that were incorrectly copied. The ones left are either as a result of duplicate spacing not copying
# or intentional when someone wrote description "is my best" continued description

@@

>>>>

#filter(annotated,span_good==F) #Note: dowm from more that were incorrectly copied. The ones left are either as a result of duplicate spacing not copying
# or intentional when someone wrote description "is my best" continued description

@@

```{r}
end <- read_csv(here(annotation_path,"post_test_annotated.csv")) |> 
  filter(!is.na(spellchecked)) |> write_csv(here(annotation_path,"post_test_pre_sbert.csv"))
